---
title: "E-learning"
output: html_notebook
---

which would the best choices for advertising?

loading resources
```{r}
library(readr)
library(dplyr)
library(stringr)
library(purrr)
```
q: Why you're using a ready-made data set instead of organizing a survey.
a: cost concerns.
q: What's this data set about.
a: satisfaction of e-learning
q: Where can this data set be downloaded.
a: dataquest,also https://github.com/freeCodeCamp/2017-new-coder-survey
```{r}
survey <- read_csv("2017-fCC-New-Coders-Survey-Data.csv")

```

Where are these new coders located. "CountryLive"
What are the locations with the greatest number of new coders. "CountryLive" frequency
How much money new coders are willing to spend on learning. 

Q: Are people interested in only one subject or they can be interested in more than one subject?
A: Some interested in only one, some intersted in more than one subject.

Q: If most people are interested in more than one subject, is this sample still representative?
A: No, this sample is not representative because most people in this survey is interested in only one subject.

Q:The focus of our courses is on web and mobile development. How many people are interested in at least one of these two subjects?
A: n = 6034
```{r}
survey2 <- survey %>%
  mutate(n_JobRoleInterest = map_dbl(JobRoleInterest, function(x) length(str_split(x, ",", simplify = TRUE)))) %>%
  select(JobRoleInterest, n_JobRoleInterest)

table(survey2$n_JobRoleInterest)

survey2%>%
  filter(str_detect(JobRoleInterest, "Web") | str_detect(JobRoleInterest, "Mobile")) %>%
           summarize(count = n())
```
drop rows is.na(JobRoleInterested), make a frequency table for CountryLive
based on the results, the two markets for advertisement is US and India

```{r}
survey %>%
  filter(!is.na(JobRoleInterest)) %>%
  group_by(CountryLive) %>%
  summarize(Count = n()) %>%
  arrange(desc(Count))
```

create MoneySpentPerMonth column
From the results, average monthly spending is the highest for US and Canada.
However, the project meant to also take into account "JobRoleInterest" to be !is.na
after this filter, the results have changed a great deal, india and Canada have similar number.

the solution for this problem is in python!

```{r}
target_country <- c("United States of America","India","United Kingdom","Canada")
survey %>%
  mutate(MonthsProgramming = ifelse(0,1,MonthsProgramming)) %>%
  mutate(MoneySpentPerMonth = MoneyForLearning/MonthsProgramming) %>%
  filter(!is.na(JobRoleInterest))%>%
  filter(!is.na(MoneySpentPerMonth)) %>%
  filter(CountryLive %in% target_country) %>%
  group_by(CountryLive) %>%
  summarize(count = n(), MeanMonthlySpent = mean(MoneySpentPerMonth))%>%
  arrange(desc(count))

survey %>%
  filter(CountryLive %in% target_country) %>%

  group_by(CountryLive) %>%
  summarize(count = n()) %>%
  arrange(desc(count))
```
